\pkg{ShinyMICE}: An Evaluation Suite for Multiple Imputation

### 2020-01-13 3.Thesis/Writeup/Thesis.Rnw

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}

@@

% For a simple illustration of basic Poisson and NB count regression the
% \code{quine} data from the \pkg{MASS} package is used. This provides the number
% of \code{Days} that children were absent from school in Australia in a
% particular year, along with several covariates that can be employed as regressors.
% The data can be loaded by
%
% <<data>>=
% data("quine", package = "MASS")
%
% and a basic frequency distribution of the response variable is displayed in
% Figure~\ref{fig:quine}.

@@

% \begin{figure}[t!]
% \centering
% <<visualization, echo=FALSE, fig=TRUE, height=5.2, width=7>>=
% par(mar = c(4, 4, 1, 1))
% plot(table(quine$Days), xlab = "Days", ylab = "Frequency", axes = FALSE)
% axis(2)
% axis(1, at = 0:16 * 5, labels = FALSE)
% axis(1, at = 0:8 * 10)
% box()
% \caption{\label{fig:quine} Frequency distribution for number of days absent
% from school.}
% \end{figure}

% As a first model for the \code{quine} data, we fit the basic Poisson regression
% model. (Note that JSS prefers when the second line of code is indented by two
% spaces.)
%
% <<poisson>>=
% m_pois <- glm(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine,
%   family = poisson)
%
% To account for potential overdispersion we also consider a negative binomial
% GLM.
%
% <<negbin>>=
% library("MASS")
% m_nbin <- glm.nb(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine)
%
% In a comparison with the BIC the latter model is clearly preferred.
% %
% <<comparison>>=
% BIC(m_pois, m_nbin)
% %
% Hence, the full summary of that model is shown below.
% %
% <<summary>>=
% summary(m_nbin)

@@

The results in this paper were obtained using \proglang{R}~3.6.2 with the \pkg{mice}~3.7.0 package. \proglang{R} itself and all packages used are available from the Comprehensive \proglang{R} Archive Network (CRAN) at \url{https://CRAN.R-project.org/}.

>>>>

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}
\SweaveOpts{engine=R, eps=FALSE, keep.source = TRUE}
<<preliminaries, echo=FALSE, results=hide>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
@

@@

% For a simple illustration of basic Poisson and NB count regression the
% \code{quine} data from the \pkg{MASS} package is used. This provides the number
% of \code{Days} that children were absent from school in Australia in a
% particular year, along with several covariates that can be employed as regressors.
% The data can be loaded by
%
% <<data>>=
% data("quine", package = "MASS")
@
%
% and a basic frequency distribution of the response variable is displayed in
% Figure~\ref{fig:quine}.

@@

% \begin{figure}[t!]
% \centering
% <<visualization, echo=FALSE, fig=TRUE, height=5.2, width=7>>=
% par(mar = c(4, 4, 1, 1))
% plot(table(quine$Days), xlab = "Days", ylab = "Frequency", axes = FALSE)
% axis(2)
% axis(1, at = 0:16 * 5, labels = FALSE)
% axis(1, at = 0:8 * 10)
% box()
@
% \caption{\label{fig:quine} Frequency distribution for number of days absent
% from school.}
% \end{figure}

% As a first model for the \code{quine} data, we fit the basic Poisson regression
% model. (Note that JSS prefers when the second line of code is indented by two
% spaces.)
%
% <<poisson>>=
% m_pois <- glm(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine,
%   family = poisson)
@
%
% To account for potential overdispersion we also consider a negative binomial
% GLM.
%
% <<negbin>>=
% library("MASS")
% m_nbin <- glm.nb(Days ~ (Eth + Sex + Age + Lrn)^2, data = quine)
@
%
% In a comparison with the BIC the latter model is clearly preferred.
% %
% <<comparison>>=
% BIC(m_pois, m_nbin)
@
% %
% Hence, the full summary of that model is shown below.
% %
% <<summary>>=
% summary(m_nbin)
@

@@

The results in this paper were obtained using \proglang{R}~\Sexpr{paste(R.Version()[6:7], collapse = ".")} with the \pkg{mice}~\Sexpr{paste(packageVersion("mice"), collapse = ".")} package. \proglang{R} itself and all packages used are available from the Comprehensive \proglang{R} Archive Network (CRAN) at \url{https://CRAN.R-project.org/}.
